\textbf{Evaluating KNN, SVR, ANN, XGBoost Regressor, Linear Regression, and Random Forest Models for Dengue Case Prediction: A Comparative Study}

### 2024-12-09 paper/main.tex
update ann methodology
Added ANN diagram

\subsubsection{Artificial Neural Network}
The model was trained with a learning rate of 0.001, utilizing the Adam optimizer to ensure efficient training. The training process was set to run for 200 epochs, with a batch size of 16, meaning 16 training samples were processed per iteration. To capture complex patterns without overfitting, a hidden layer consisting of 64 neurons was chosen. The architecture followed a Sequential Neural Network design, incorporating an input layer, one hidden layer, and an output layer. Additionally, early stopping was implemented to prevent overfitting by monitoring the validation performance during training.

>>>>

\subsubsection{Artificial Neural Network}
\begin{figure}[h!]
	\centering
	\includegraphics[width=1\linewidth]{image/ANN diagram.png}
	\caption{ANN Flow Diagram}
	\label{fig:annflow}
\end{figure}
The model was trained with a learning rate of 0.001, utilizing the Adam optimizer to ensure efficient training. The training process was set to run for 200 epochs, with a batch size of 16, meaning 16 training samples were processed per iteration. To capture complex patterns without overfitting, a hidden layer consisting of 64 neurons with a ReLU activation function was chosen. The architecture followed a Sequential Neural Network design, incorporating an input layer, one hidden layer, and an output layer. Additionally, early stopping was implemented to prevent overfitting by monitoring the validation performance during training.
